\documentclass[11pt]{jsarticle}
\begin{document}
%------ここまで表紙------%
\section{Single-sex schools are not necessary.}
\noindent
%挨拶
H: Hello.\\
I: Hello.\\
H: In my memory, you went to an all boys high school, right?\\
I: Yes, I had a good time in my school.\\
%男女が同じ空間にいる
H: I see, but you had a more good time if you went to coeducational school.
I went to a coeducational school. I think ``Single-sex schools are not necessary.''
in coeducational shcools, boys and girls are always in the same space as Waseda University.
This has a lot of merit, because we can communicate with everyone.
For example, we can learn how to contact, we can join many events with girls.
When I was in high school, we played relay with girls at sports festival.
But I think single-sex schools don't have these events. \\
%
I: There are a lot of events only in single sex schools. If teachers make a plan to go to the mountain,
they have to think about girls’ physical strength.
However, if there are only men in the school, they don’t have to think about it and can carry out such a hard plan.\\
H: We can spend a relatively moral school life, because there are girl's eye.
We can't act silly, such as talking dirty topics.\\
%
I: We have freedom to do anything. For example, we can say clearly and aloud even if it is a dirty topic.
Some teachers sometimes talk about it. Some people say that it is not good for learning how to behavior, but it is not true.
They can say without hesitation, so they experience how to hurt others’ feelings.
Therefore, they usually observe social morals and know how to express their feeling.\\
H:And we come to no longer have any ideal image about woman.
We tend to think about women as diligent, clean and other many positive images.
I feel bad for girls, but actually, it is not true.
When we start working, there are many women.
Then we'll must get used to women, so students should be in coeducational school, not all boys, not all girls.\\
I: I disagree with this opinion because students can do their hobby without thinking what women feel about their hobby.
For example, when I was a high school student in a single-sex school,
many students enjoyed going to see a pop idol, playing video games too much or making a model.
They are called “otaku”. 
Many people are interested in such hobbies, but many women think of their actions as strange and some men give up enjoying.
However, many students in a single-sex school enjoyed their hobby and don’t have to be embarrassed to enjoy
because there are no girls in single sex schools and they can talk about their hobbies in their school.

\section{You will be happier if you stay unmarried.}
\noindent
I: Do you want to marry someday?\\
H: Yes, I want to marry.\\
%自由に時間を使える
I: I think you will be happier if you stay unmarried, because people can use free time for themselves.
For example, if a man marries and has children, he will help them with their homework,
take them to a kindergarten or cram school, or make meals for children.
Therefore, he will use most of the time for taking care of children.
Also, the number of people in one family is smaller and smaller, so fewer and fewer people help parents who raise children.
Parents can’t make free time because they can’t even find people who can look after their children for a while. \\
%
H: My opinion is opposite of yours.
First, You said that unmarried person have more free time than married.
However, if you marry, you can share houcework with your wife.
For example, cooking, washing, xxx. 
There are so many tasks to live in your houce. Unmarried person must do its tasks by yourself.\\
%
I: People can easily control their stress. 
If a man married, he will think about his partner. 
But they usually conflict with each other because their sexes are different.
Also, when they have children, they sometimes must listen children’s trouble and tell them some advice.
These events are very stressful. If unmarried, they can concentrate on working. They will not worry about a lot of things.\\
H: Umm..., you say xxx
I understand your opinion, but married persons has how to reduce their stress.
They can consult with his partner.\\
%もっとお金を使える
I: People can use free money for themselves. 
People may argue with their partner about how to share money parents earn.
Mostly, a man loses a fight, and a woman has the initiative for using money.
After having children, parents must use a lot of money for children, such as education or medical care.
Some parents become poor and poor.
But, if people stayed unmarried,
they can save a lot of money and use it for hobbies or something unexpected that they must pay a lot of money. 
H: Married person has merits, too. One of it, when you are old, also you need any help to live.
Then, your children will look after you.
Recentry, lonely death is a important issue, so it is often discussed in Japan.
To solve this problem, live with family. 

互いに和解
end
\end{document}